\documentclass[a4paper, 12pt]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}

\graphicspath{ {images/} }

\title{Fail-Safe Cloud Tournament Engine Project Plan}
\author{Kyle Chapman (20703236)}
\date{March 2020}

\begin{document}

\maketitle

\section{First Semester Goals}

\subsection{March}

\begin{itemize}
	\item Finish fixing the current Cloud Tournament Engine.
	\item Deploy to Kubernetes (K8S).
	\item Add logging to Kubernetes and the code base.
\end{itemize}

\subsection{April}

\begin{itemize}
	\item Set up a basic tournament engine that can run and manage matches.
	\item Deploy to Kubernetes (K8S).
	\item Release an alpha to the students for testing purposes.
\end{itemize}

\subsection{May}

\begin{itemize}
	\item Make final changes for the first demo.
	\item Implement all required features for the new Cloud Tournament Engine.
	\item Start extensive testing.
\end{itemize}

\subsection{June}

\begin{itemize}
	\item Continue extensive testing.
	\item Start extensive documentation.
\end{itemize}

\section{Second Semester Goals}

\subsection{July}

\begin{itemize}
	\item Continue extensive documentation.
	\item Tidy up code base.
	\item Improve user experience and the user interface.
\end{itemize}

\subsection{August}

\begin{itemize}
	\item Finish documentation and testing.
	\item Start writing final report.
\end{itemize}

\subsection{September - November}

\begin{itemize}
	\item Start making poster.
	\item Start preparing for the demo.
\end{itemize}

\section*{Calendar Plan}

I have attached a proposed project plan in calendar format on the next page.

\end{document}
